Stack Safety is a Security Property

### 2021-04-13 tex/main.tex
A few more things in the abstract

We propose formal criteria for stack safety, phrased in terms of
language-based security: a combination of an integrity property (``each
caller's stack frame is held invariant by the callee'') and a confidentiality
property (``the callee's behavior is insensitive to differences in the
caller's state'').
% These properties are sensible even in the presence of
% abnormal control flow.\apt{Is this important enough to mention here?}
% BCP: I think not in the abstract, but maybe in the intro.
% We further apply\apt{what does this mean? we didn't
%  invent it} a straightforward notion of
% ``well-bracketed control flow'' that restricts control flow to the
% typical pattern of matched calls and returns.
%
We argue that these criteria match common intuitions (1) by showing that
they are violated by a variety of intuitively unsafe examples and (2) by
using property-based random testing to check that appropriate variants of
the criteria are actually enforced by the stack-safety ``micro-policies''
proposed by~\citet{DBLP:conf/sp/RoesslerD18}.  Specifically, Roessler and
dehon's ``eager'' micro-policy, which catches violations as early as
possible, enforces simple ``stepwise'' versions of our confidentiality and
integrity properties, while their more performant ``lazy'' micro-policy
enforces weaker, more extensional ``observational'' variants of the
properties.

\bcp{We should mention stack data and coroutines, I think?}

>>>>

We propose formal criteria for stack safety, phrased in terms of
language-based security: a combination of an integrity property (``each
caller's stack frame is held invariant by the callee'') and a confidentiality
property (``the callee's behavior is insensitive to differences in the
caller's state'').
% These properties are sensible even in the presence of
% abnormal control flow.\apt{Is this important enough to mention here?}
% BCP: I think not in the abstract, but maybe in the intro.
% We further apply\apt{what does this mean? we didn't
%  invent it} a straightforward notion of
% ``well-bracketed control flow'' that restricts control flow to the
% typical pattern of matched calls and returns.
%
We argue that these criteria match common intuitions (1) by showing that
they are violated by a variety of intuitively unsafe examples and (2) by
using property-based random testing to check that appropriate variants of
the criteria are actually enforced by the stack-safety ``micro-policies''
proposed by~\citet{DBLP:conf/sp/RoesslerD18} (and {\em not} enforced by
broken versions of these enforcement mechanisms).  Specifically, Roessler
and Dehon's ``eager'' micro-policy, which catches violations as early as
possible, enforces the basic ``stepwise'' versions of our confidentiality
and integrity properties, while their more performant ``lazy'' micro-policy
enforces weaker, more extensional ``observational'' variants of the
properties.

\bcp{We should mention stack data and coroutines, I think?  Maybe in the
  context of an expectation-lowering hedge, like:}%
For the sake of simplicity, most of our presentation assumes a RISC-V
machine architecture with a basic subroutine calling convention, where
parameters are passed in registers.  We also show how stack-allocated
parameter passing and coroutines can be accommodated.
